Halving the cost of quantum addition

### 2017-09-26 paper.tex
Incorporating comments from Dmitri Maslov - Dmitri objected to the email thread with Austin being construed as stating a conjecture. Removed. - Added n-control NOT as an example.

The leading factor of 8 in the T-count of an $n$-bit adder has stood for over a decade \citep{Barenco1995, Cuccaro2004}, and has been conjectured to be optimal \cite{AustinDiscussionsAndEmails2017}.
We disprove this conjecture with a construction based on the temporary logical-AND, which combines ideas from both the matched-phase-error construction and the ancilla-and-fix-up construction.
The temporary logical-AND halves the number of T gates needed to perform Toffoli gates that appear in compute/uncompute pairs, and thereby halves the T-count of the Cuccaro adder from $8n + O(1)$ to $4n + O(1)$.

@@

Toffolis also appear in compute/uncompute pairs in quantum circuits rooted in physics instead of abstract mathematics.
For example, we used temporary logical-ANDs to cut the projected T-count of a step in a simulation algorithm under development by nearly 30\% \citep{RyanEmails2017}.

@@

We thank Austin Fowler for sampling the opinions of other researchers, for assistance locating references, and for comments that significantly improved this paper.
We thank Dave Bacon for comments that significantly improved this paper.

>>>>

The leading factor of 8 in the T-count of an $n$-bit adder has stood for over a decade \citep{Barenco1995, Cuccaro2004, AustinDiscussionsAndEmails2017}.
We improve the leading factor with a construction based on the temporary logical-AND, which combines ideas from both the matched-phase-error construction and the ancilla-and-fix-up construction.
The temporary logical-AND halves the number of T gates needed to perform Toffoli gates that appear in compute/uncompute pairs, and thereby halves the T-count of the Cuccaro adder from $8n + O(1)$ to $4n + O(1)$.

@@

As another example, note that the temporary logical-AND can perform NOT gates with many controls by iteratively combining the controls down to a single representative ancilla.
The representative ancilla is then used to control a CNOT onto the target qubit.
Overall this takes $4n-4$ T gates, equivalent to previous work \cite{Jones2013}.
As when replacing Toffoli gates in compute/uncompute pairs with a temporary logical-AND, the ancilla representing the $n$ controls should be kept and used multiple times whenever possible (instead of being uncomputed and recomputed).

Finally, we note that Toffolis also appear in compute/uncompute pairs in quantum circuits rooted in physics instead of abstract mathematics.
For example, we used temporary logical-ANDs to cut the projected T-count of a step in a simulation algorithm under development by nearly 30\% \citep{RyanEmails2017}.

@@

We thank Austin Fowler for sampling the opinions of other researchers, for assistance locating references, and for comments that significantly improved this paper.
We thank Dave Bacon and Dmitri Maslov for comments that significantly improved this paper.
